\vspace{.25in}
\begin{center}
    \large{\textbf{Acknowledgement}}
    \vspace{0.3in}
\end{center}

\begin{center}
    \begin{minipage} {\textwidth}

        \setstretch{1.0}
        \setlength{\parindent}{10pt}
        \setlength{\parskip}{12pt}

        \tolerance=1
        \emergencystretch=\maxdimen
        \hyphenpenalty=10000
        \hbadness=10000

        \noindent The success accomplished in this seminar would not have been possible without the
        timely help and guidance rendered by many people to whom I feel obliged and grateful.

        \noindent First of all, I would like to express my sincere thanks to our beloved principal
        \textbf{Dr.~Prince~A}, for his support and encouragement.

        \noindent I use this occasion to express my thanks to \textbf{Dr.~David Solomon George},
        Head of Electronics and Communication Engineering Department for his continuous
        encouragement to fulfill my seminar.

        \noindent I am thankful to my seminar coordinators \textbf{Dr. Sajeev G P},
        \textbf{Dr. Nelsa Abraham} and my guide \textbf{Prof. Sujithamol S}, for their valuable
        suggestions, inspiration and motivation throughout the seminar work.


        \noindent I am also thankful to all the teaching and non teaching staff in Electronics and
        Communication Department for their timely assistance. I thank my parents and friends for
        their kind cooperation and suggestions which helped me very much for the accomplishment of
        this seminar work.

        \noindent Above all, I would like to express my sincere thanks to the Almighty God, who
        empowered me to fulfill this work, by showering his abundant grace and mercy.

        \vspace{0.5in}

    \end{minipage}
\end{center}

\begin{center}
    \begin{minipage}[t] {0.60\textwidth}
        \raggedright
        Rajiv Gandhi Institute of Technology, \\
        Sept 2025

    \end{minipage}
    \hfill
    \begin{minipage}[t] {0.35\textwidth}
        \raggedleft
        \author

    \end{minipage}

\end{center}
